\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}

\begin{document}
\section*{{2025 USAMO Problems/Problem 3}}
Source: AoPS Wiki

\subsection*{Solution}
Alice has a winning strategy: Choose $\mathcal S$ to be the set of of points strictly outside the disk with diameter $PQ$ . Then two cities $A$ and $B$ have a road between them if and only if every other city is outside the closed disk with diameter $AB$ . Note that this condition is equivalent to the angle $\angle ACB$ being acute for every other city $C$ . We need to prove that no matter how Bob chooses cities, No roads cross, and All cities are connected. We first prove (1). Suppose for the sake of contradiction that there are roads between $A$ and $C$ and between $B$ and $D$ , and that these roads cross. Then $ABCD$ is a convex quadrilateral, because its diagonals intersect. Now, recall our condition for the existence of roads between $A$ and $C$ and between $B$ and $D$ : We must have that the angles $\angle ABC$ , $\angle BCD$ , $\angle CDA$ , and $\angle DAB$ are all acute. Because $ABCD$ is a convex quadrilateral, these angles are the interior angles. Then the sum of the interior angles of $ABCD$ is less than $360^\circ$ , a contradiction with the fact that the sum of the interior angles of a quadrilateral is always $360^\circ$ . $\rightarrow \leftarrow$ We next prove (2). We use induction on the Euclidean distance between cities. Our base case is that two cities are less than $1$ away from each other. If this is the case, then they are the same city, and so the empty path connects them. Now, suppose for the sake of induction that any two cities less than $\sqrt n$ away from each other have a finite path between them. We will show the same is true for $\sqrt{n + 1}$ . Consider any two distinct cities $A$ and $B$ less than $\sqrt{n + 1}$ away from each other. If there is a road between them, we are done. Otherwise, there must be some third city $C$ for which $\angle ACB \geq 90^\circ$ . [asy] import markers; size(12cm); pair A = (-1,0); pair B = (1,0); pair O = (0,0); // Point C in the upper-left of the disk pair C = dir(120) * 0.8; draw(circle(O,1)); draw(A--B, dashed); draw(A--C); draw(C--B); label("less than $\sqrt{n+1}$", A--B, S); markangle(radius=10, A, C, B); dot(A); dot(B); dot(C); label("$A$", A, W); label("$B$", B, E); label("$C$", C, N); [/asy] By the Law of Cosines, we get that \[\overline{AB}^2 \geq \overline{AC}^2 + \overline{CB}^2.\] Because no two cities are closer than $1$ away from each other, both $\overline{AC}$ and $\overline{CB}$ are at least $1$ . So, \[\overline{AC}^2 \leq \overline{AB}^2 - \overline{CB}^2 < (n + 1) - 1 = n.\] Hence, by the inductive hypothesis, there is a finite path from $A$ to $C$ . Likewise, there is a finite path from $C$ to $B$ . Joining these paths together, we get a finite path from $A$ to $B$ , as desired. Hence, any two cities, no matter their distance apart, have a finite path connecting them. $\square$ Note: The graph of roads constructed by Alice's choice of $\mathcal S$ is called the Gabriel graph .

\end{document}
