\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}

\begin{document}
\section*{{2020 USAMO Problems/Problem 2}}
Source: AoPS Wiki

\subsection*{Solution}
Take one vertex of the cube as origin and establish 3D coordinates along the cube's edges. Define a beam as $x-dir$ if its long edge is parallel to x-axis. Similarly for $y-dir$ and $z-dir$ . Define a beam's location as (direction, ( $1 \times 1$ face's location in 2D coordinate). For example, (y, 2, 4) indicates the beam with vertex (1, 0, 3) and (2, 2020, 4) Apparently $x$ beam needs the other $x$ or $y$ beams to touch its $xy$ faces, $x$ or $z$ beams to touch its $xz$ faces. Similarly for $y$ and $z$ beam. If there are only 1-dir or 2-dirs beams, it is easy to approve that $2020 \times 2020$ is the minimal number beams. (for example, if only use $x-dir$ and $y-dir$ beams, all the $x-dir$ beams's xz faces can only be touched by $x-dir$ beams. In the other word, $2020 x-dir$ beams will be stacked to meet xz faces touch requirements in that xz layer) Consider cases with all $3-dirs$ beams.
WLOG there is a $x-dir$ beam and it needs $x-dir$ or $y-dir$ beams to touch its $xy$ faces (unless it touches the cube surface). And this $y-dir$ beam also needs a $x-dir$ or $y-dir$ to touch it's $xy$ faces. And so on until one which touches cube surface. So from $xy$ face perspective, it needs $2020$ beams. Similarly from $xz$ and $yz$ face perspective, it also needs $2020$ and $2020$ beams. Consider one beam has four $1 \times 2020$ faces and it can be counted twice. So there should be at least $2020 \times 3 \div 2=3030$ beams. Here is one solution with 3030 beams. $(x, 1, 1),\ (y, 1, 2),\ (z, 2, 2),$ $\cdots ,$ $(x, (2n+1), (2n+1)),\ (y, (2n+1), (2n+2)),\ (z, (2n+2), (2n+2)),$ $\cdots ,$ $(x, (2019, 2019)),\ (y, 2019, 2020),\ (z, 2020, 2020)$ 2020 USAMO ( Problems • Resources ) Preceded by Problem 1 Followed by Problem 3 1 • 2 • 3 • 4 • 5 • 6 All USAMO Problems and Solutions

\end{document}
